Notebook template

### 2024-03-18 scripts/examples/manuscript/index.qmd
fix(scripts): comment examples authors Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: "Notebook template"
toc: true
number-sections: true
highlight-style: pygments
csl: bibstyle.csl
format:
  nature-pdf:
    natbibstyle: sn-nature
    classoption: 
      - lineno
    cite-method: citeproc
    keep-tex: true
  html:
    code-fold: true
    html-math-method: katex
  docx: default
execute: 
  cache: true
  keep-ipynb: true
author:
  - name: Author One
    affiliations:
      - name: Harvard University
        id: 1
        department: Department of Government
        address: 1737 Cambridge Street
        city: Cambridge
        state: MA
        postal-code: 02138
      - name: Harvard University
        id: 2
        department: Department of Statistics
        address: 1 Oxford Street
        city: Cambridge
        state: MA
        postal-code: 02138
    attributes:
      equal-contributor: true
  - name: Author Two
    affiliations:
      - name: Yale University
        id: 3
        department: Department of Political Science
        address: 115 Prospect Street
        city: New Haven
        state: CT
        postal-code: 06511
    email: corresponding@email.com
    attributes:
      equal-contributor: true
      corresponding: true
  - name: Author Three
    affiliations:
      - ref: 1
abstract: |
  The abstract serves both as a general introduction to the topic and as a
  brief, non-technical summary of the main results and their implications.
  Authors are advised to check the author instructions for the journal they are
  submitting to for word limits and if structural elements like subheadings,
  citations, or equations are permitted.
keywords: [template, demo]
bibliography: references.bib
jupyter:
  jupytext:
    cell_metadata_filter: all
    cell_metadata_json: true
    notebook_metadata_filter: all
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: '1.0'
      jupytext_version: 1.16.0
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
---

>>>>

---
title: "Notebook template"
toc: true
number-sections: true
highlight-style: pygments
csl: bibstyle.csl
format:
  nature-pdf:
    natbibstyle: sn-nature
    classoption: 
      - lineno
    cite-method: citeproc
    keep-tex: true
  html:
    mainfont: Latin Modern Roman
    code-fold: true
    html-math-method: katex
  docx: default
execute: 
  cache: true
  keep-ipynb: true
author:
  - name: Pyrovelocity Authors
  # - name: Qian Qin
  #   affiliations:
  #     - name: Broad Institute of MIT and Harvard
  #       department: Broad Institute of MIT and Harvard
  #       id: 1
  #       city: Cambridge
  #       state: MA
  #   email: qqin@broadinstitute.org
  #   attributes:
  #     equal-contributor: true
  # - name: Cameron Smith
  #   affiliations:
  #     - ref: 1
  #     - name: Harvard Medical School
  #       id: 2
  #       department: Department of Pathology
  #       city: Boston
  #       state: MA
  #     - name: Massachusetts General Hospital
  #       id: 3
  #       department: Molecular Pathology Unit, Center for Cancer Research
  #       city: Boston
  #       state: MA
  #   email: cameron.smith@mgh.harvard.edu
  #   attributes:
  #     equal-contributor: true
  # - name: Luca Pinello
  #   affiliations:
  #     - ref: 1
  #     - ref: 2
  #     - ref: 3
  #   email: lpinello@mgh.harvard.edu
  #   attributes:
  #     corresponding: true
abstract: |
  The abstract serves both as a general introduction to the topic and as a
  brief, non-technical summary of the main results and their implications.
  Authors are advised to check the author instructions for the journal they are
  submitting to for word limits and if structural elements like subheadings,
  citations, or equations are permitted.
keywords: [template, demo]
bibliography: references.bib
jupyter:
  jupytext:
    cell_metadata_filter: all
    cell_metadata_json: true
    notebook_metadata_filter: all
    text_representation:
      extension: .qmd
      format_name: quarto
      format_version: '1.0'
      jupytext_version: 1.16.0
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
---
